---
title: "Assignment 8"
subtite: "Alex Reich's Homework"
output: html_notebook
---

Task 1: Heat Maps


```{r}
library(ggplot2)
library(wesanderson)
library(tvthemes)
library (tidyverse)
library (dplyr)
library (cowplot)
library (viridis)
NPGE_PDO.dat <- read.csv("/Users/alexandrareich/Desktop/DataVIzFish/Work_dir/npgo-pdo.csv")
```

Heat Map 1: Show NPGO by month and year
```{r}
ggplot(data=NPGE_PDO.dat)+aes(x= Year,  y= Mon, fill=NPGO)+ scale_fill_viridis()+theme_cowplot()+geom_tile()
```

```{r}
ggplot(data=NPGE_PDO.dat)+aes(x= Year,  y= Mon, fill=NPGO)+ scale_fill_avatar(palette = "WaterTribe", type="continuous")+theme_avatar() +geom_tile()
```

Heat Map 2:
```{r}
ggplot(data=NPGE_PDO.dat)+aes(x= Year,  y= Mon, fill=PDO)+ scale_fill_avatar(palette = "EarthKingdom", type="continuous")+theme_avatar() +geom_tile()
```
Heat Map 3
```{r}

```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

